Make any stupid plot you want

### 2021-04-14 draft/sections/math.tex
dbase figure

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/k_different_types.png}
    \caption{The topological base space \dbase\ encodes the connectivity of the data space, for example if the data is independent points or on a plane or a sphere}
    \label{fig:base_space_types}
\end{figure}
As illustrated in figure~\ref{fig:base_space_types}, \dbase\ is akin to an indexing space into \dtotal\ that describes the structure of \dtotal.  \dbase\ can have any number of dimensions and can be continuous or discrete.

@@

Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every $\dbasepoint \in \dbase$ has a corresponding fiber $\dfiber_k$\cite{QuotientSpaceTopology2020}. In figure~\ref{fig:base_space_div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping $\pi: \dtotal\rightarrow \dbase$ is the closed interval $\left[0,1\right]$. 
As with fibers and monoids, we can decompose the total space into components $\pi:\dtotal_i\rightarrow \dbase$ where
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
which is a decomposition of \dfiber. The \dbase\ remains the same because the connectivity of records does not change just because there are fewer elements in each record.
\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        \caption{}
        \label{fig:base_example_discrete}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \caption{}
        \label{fig:base_example_continuous}
    \end{subfigure}
    \caption{These two datasets have the same (time, temperature) fiber. In figure~\ref{fig:base_example_discrete} the total space \dtotal\ is discrete over points $\dbasepoint \in \dbase$, meaning the records in the fiber are also discrete. In figure~\ref{fig:base_example_continuous} \dtotal\ lies over the continuous interval \dbase, meaning the records in the fiber are sampled from a continuous space.} 
    \label{fig:base_example}
\end{figure}

The datasets in figure~\ref{fig:base_example} have the same fiber of (temperature, time). In figure~\ref{fig:base_example_discrete} the fibers lie over discrete \dbase\ such that the records in the datasets in the fiber bundles are discrete. The same fiber in figure~\ref{fig:base_example_continuous} lies over a continuous interval \dbase\ such that the records are samples from a continuous function defined on \dbase. By encoding this continuity in the model as \dbase\, the data model now explicitly carries information about its structure such that the implicit assumptions of the visualization algorithms are now explicit. The explicit topology is a concise way of distinguishing visualizations that appear identical, for example heatmaps and images.

>>>>

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/k_different_types.png}
    \caption{The topological base space \dbase\ encodes the continuity of the data space, for example if the data is discrete points or lies on a plane or a sphere}
    \label{fig:base_space_types}
\end{figure}
As illustrated in figure~\ref{fig:base_space_types}, \dbase\ is akin to an indexing space into \dtotal\ that describes the structure of \dtotal.  \dbase\ can have any number of dimensions and can be continuous or discrete.

@@

Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every $\dbasepoint \in \dbase$ has a corresponding fiber $\dfiber_k$\cite{QuotientSpaceTopology2020}. In figure~\ref{fig:base_space_div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping $\pi: \dtotal\rightarrow \dbase$ is the closed interval $\left[0,1\right]$. 
As with fibers and monoids, we can decompose the total space into components $\pi:\dtotal_i\rightarrow \dbase$ where
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
which is a decomposition of \dfiber. The \dbase\ remains the same because the connectivity of records does not change just because there are fewer elements in each record.
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/base.png}
    \caption{These two datasets have the same (time, temperature) fiber, but different continuities. The dataset on the left consists of discrete records, while the records in the dataset on the right sampled from a continuous space.} 
    \label{fig:base_example}
\end{figure}

The datasets in figure~\ref{fig:base_example} have the same fiber of (temperature, time). The dot represents a discrete base space \dbase, meaning that every dataset encoded in the fiber bundle has discrete continuity. The line is a representation of a 1D continuity, meaning that every dataset in the fiber bundle is 1D continous. By encoding this continuity in the model as \dbase\, the data model now explicitly carries information about its structure such that the implicit assumptions of the visualization algorithms are now explicit. The explicit topology is a concise way of distinguishing visualizations that appear identical, for example heatmaps and images.
